The Processing of American Indian/Alaska Native Children through non-Tribal

### 2019-12-19 ms.rmd
update

>>>>

This report examines how american indian children are processed through us child welfare systems. it explores the likelihood that american indian children eventually end up in foster care, end up in foster care with non-indian foster parents, or see the rights of their parents terminated. I compare these pathways through the foster care system to the pathways experienced by white and African American children.

I use the 2003 - 2016 AFCARS and NCANDS to calculate period lifetables for lifetime risk of investigation, substantiation, placement, placement into a non-ICWA compliant foster placement, and termination of parental rights. Each of these tables provides an estimate of the cumulative risk of experiencing the event before age 18 if risk-levels observed during the reported period remain constant.

## What am I estimating
